Energy and exergy analysis of a cruise ship

### 2017-07-19 Manuscript/Manuscript.tex
pre-processing manuscript

This section should be written by FA :-)

>>>>

The operational data was collected on board from the ships' machine logging and surveillance system. The on board database tool exported all logging points to Excel-97 files, and due to the extensive amount of data points the export was divided in to 15 individual Excel-files consisting of a total 665 MB. The exported raw-data from the ship was over a time span of a full year and in most data-points in 15-min average. The Excel-files were processed in the Pandas library which is a high performance data analysis tool in Python [**INSERT REF TO PANDAS**]. A new structured naming of headers and a consistent time frequency over all data points were created in a HDF5 table database which is the base for the analysis.
